Poseidon Adventure

### 2019-05-11 docs/index.Rmd
Update index.Rmd
add fail filename
add new length comp file

@@

<a href="https://sgaichas.github.io/poseidon-dev/TrueLengthCompTest.html" target="_blank">Defeated by length compositions - May 8-9, 2019</a>

>>>>

May 11: Changes to `atlantisom::sample_fish` and new `atlantisom::aggregateDensityData` functions seem to work. See below under [Length compositions].

@@

<a href="https://sgaichas.github.io/poseidon-dev/TrueLengthCompTest_fail.html" target="_blank">Defeated by length compositions - May 8-9, 2019</a>

Better when you do:

<a href="https://sgaichas.github.io/poseidon-dev/TrueLengthCompTest.html" target="_blank">Victory: length compositions - May 11, 2019</a>
